Bioverse: Potentially Observable Exoplanet Biosignature Patterns Under the UV Threshold Hypothesis for the Origin of Life

### 2024-12-12 src/tex/ms.tex
add oxidation states

\subsubsection{Atmosphere transmission}
We do not take into account absorption of UV radiation by the planetary atmosphere.
Theoretical work suggests that the atmosphere of prebiotic Earth was largely transparent at \gls{NUV} wavelengths with the only known source of attenuation being Rayleigh scattering~\citep{Ranjan2017,Ranjan2017c}.
We thus approximated surface UV flux using top-of-atmosphere fluxes.
If there are planets in a sample that do not have a transparent atmosphere at \gls{NUV} wavelengths and require higher fluxes for abiogenesis, the fraction of inhabited planets in the sample will be lower.
However, these planets will not pollute the below-threshold subsample, as they will not be able to host life under the UV~Threshold Hypothesis.
Exoplanet surveys focusing on highly irradiated planets offer an opportunity to constrain the typical oxidation state of rocky exoplanets, providing insights into the average composition of their secondary atmospheres~\citep{Lichtenberg2024}.

>>>>

\subsubsection{Atmosphere transmission}
We do not take into account absorption of UV radiation by the planetary atmosphere.
Theoretical work suggests that the atmosphere of prebiotic Earth was largely transparent at \gls{NUV} wavelengths with the only known source of attenuation being Rayleigh scattering~\citep{Ranjan2017,Ranjan2017c}.
We thus approximated surface UV flux using top-of-atmosphere fluxes.
If there are planets in a sample that do not have a transparent atmosphere at \gls{NUV} wavelengths and require higher fluxes for abiogenesis, the fraction of inhabited planets in the sample will be lower.
However, these planets will not pollute the below-threshold subsample, as they will not be able to host life under the UV~Threshold Hypothesis.
Exoplanet surveys focusing on highly irradiated planets offer an opportunity to constrain the typical oxidation state of rocky exoplanets, providing insights into the average composition of their secondary atmospheres~\citep{Lichtenberg2024}.
This is particularly relevant for prebiotic worlds, as varying oxidation states significantly perturb the classical habitable zone concept~\citep{Nicholls2024} and also influence surface \gls{UV} levels through changing atmospheric transmission.
Optimally, the atmospheric composition of young rocky protoplanets will be probed to constrain the possible range of atmospheric and mantle oxidation states during early planetary evolution by future direct imaging concepts~\citep{Cesario2024}.
